%-------------------------
% Resume in Latex
% Author : Thomas Okubo
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Thomas Taichi Okubo} \\ \vspace{1pt}
    \small (19)99346-7367 $|$ \href{mailto:tai.okubo93@gmail.com}{\underline{tai.okubo93@gmail.com}} $|$ 
    % \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
    \href{https://github.com/thomasokubo}{\underline{github.com/thomasokubo}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer III}{Sep. 2022 -- Present}
      {QuintoAndar}{Campinas, SP - Brasil}
      \resumeItemListStart
        \resumeItem{Redesigned the visit journey for brokers, leading to a more efficient process and an improved user experience.}
        \resumeItem{Designed and implemented new lead distribution strategies for brokers, which enhanced the conversion rate from scheduled visits to offers sent}
        \resumeItem{Monitored the health of applications and excelled at debugging using logs, tracing, and alerts}
        \resumeItem{Improved the performance of SQL database queries, leading to faster response times}
        \resumeItem{Provided feedback and guidance to other engineers to help them grow and improve their skills}
        % \resumeItem{Collaborate closely with the stakeholders to streamline processes and develop new strategies}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{Sep. 2021 -- Aug. 2022}
      {QuintoAndar}{Campinas, SP - Brasil}
      \resumeItemListStart
        \resumeItem{Designed and led the development of a system for managing sale negotiations, including architecture design, database modeling, and task breakdown.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer I}{Aug. 2019 -- Aug. 2021}
      {QuintoAndar}{Campinas, SP - Brasil}
      \resumeItemListStart
        \resumeItem{Developed a Java application to automate the credit analysis, reducing the manual screening time}
        \resumeItem{Redesigned the login flow using Java (Spring) and React, providing a seamless journey}
        \resumeItem{Built a negotiation chat system with Python (Django) and React, enabling direct communication between buyers and sellers, minimizing the need for CX's intervention}
      \resumeItemListEnd
    

    \resumeSubheading
      {Software Development Specialist}{Jan. 2019 -- Jul. 2019}
      {Daitan Group}{Campinas, SP - Brasil}
      \resumeItemListStart
        \resumeItem{Automated the test pipeline using Robot Framework}      
        \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Intern}{Jan. 2018 -- Dec. 2018}
      {Daitan Group}{Campinas, SP - Brasil}
      \resumeItemListStart
        \resumeItem{Developed a REST API in Java for monitoring individuals and entities against Risk \& Compliance data, offering features like ongoing monitoring, customizable screening preferences, and bulk screening.}
        \resumeItem{Wrote regression tests with Cucumber and Ruby}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Unicamp}{Campinas, SP - Brasil}
      {Bachelor of Computer Engineering}{Mar. 2018 -- Dec. 2018}
    \resumeSubheading
      {McNair Secondary School}{Richmond, BC - Canada}
      {High School Exchange Program}{Sep. 2010 -- Jan. 2011}
  \resumeSubHeadingListEnd


%-----------CONTEST-----------
\section{Contest}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ACM-ICPC South America}{Piracicaba, SP - Brasil}
      {Brazil Regionals}{Aug. 2017}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java \href{https://www.youracclaim.com/badges/f59280fe-5fcc-485c-8ce9-d3ea07fba82b/linked_in_profile}{\underline{(Oracle Certificate Associate SE8)}}, Javascript, C/C++, Python (Basic)} \\
     \textbf{Frameworks}{: Spring, React, Express, Django} \\
     \textbf{Databases}{: PostgresSQL, MySQL, Firestore, Redis, MongoDB} \\
     \textbf{Cloud}{: Google Cloud Platform (lambdas, Pub/Sub), AWS (SNS, SQS, S3), Kafka} \\
     \textbf{Observability}{: Kibana, Grafana, Instana, Sentry} \\
     \textbf{Developer Tools}{: Git, Docker} \\
     \textbf{Testing}{: JUnit, Cucumber, React Testing Library}
    }}
 \end{itemize}


%-----------IDIOMS-----------
\section{Idioms}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Portuguese}{: Native} \hspace{1cm}
     \textbf{English}{: Advanced}  \hspace{1cm}
     \textbf{Spanish}{: Basic} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
